Programming Assignment 2

### 2015-04-02 paper.tex
Updated member assignments
Filled out the overview and encoding sections of the lvq network

\section{Hamming-Max Network}
The Hamming-Max was fairly straight forward to construct.  We first created the hammingnet portion which was given the input vector and weight matrix.  It computed the hamming distance of the input from each column vector prototype of the weight matrix, storing those values in an output vector, equal in width to the weight matrix.  We then constructed the Maxnet which was given the Hammingnet output as a parameter.  It subtracts 1 from each element until a single zero value is found, declaring it the smallest hamming distance.  This index represents the prototype which is most similar to the input, suggesting the input must be of this classification.

\subsection{Image Encoding}
Deciding how to encode our images was a bit tricky.  We played with a few different ways of obtaining image outlines however, we decided for this network, simply finding images already in outline form would be best.  We removed inner detail from these outlines and ran them through a program we wrote.  First, the images are resized so that they are all one standard size,  the images are then grayscaled and run through a threshhold function so that a clear outline of black on white is present.  To establish the prototypes for our weight matrix, we added the values of each representative image matrix to eachother, then averaged the values and processed the result as before.  We adjusted our threshhold function to maintain clarity.  We found that visually, too small a size diminshed image definition, while too large was time and resource intensive and lacked definitive shape for the prototype matrix.

@@

\section{LVQ}

@@

\subsubsection{Project Report}
Jonathan was tasked with the Hamming/Max section.

@@

\subsection{Skyler "Scrub on the Frub" Manzanares}
\subsubsection{Programming}
Skyler implemented the formatting of centroid images to the weight matrix to be fed into the Hamming/MAX network. He also did extensive work creating the functions that read in and format images. Skyler was also responsible for implementing
the HAM network.

@@

\subsection{William Fong}
\subsubsection{Programming}
William worked to create the Max layer of the Hamming/Max network and coordinate 
inputs and outputs of the various layers, summing all components together to create a working Hamming/Max network. William was also in charge of implementing the BAM network.

\subsubsection{Project Report}
William was tasked to the BAM section.

>>>>

\section{Hamming-Max Network}
The Hamming-Max was fairly straight forward to construct.  We first created the hammingnet portion which was given the input vector and weight matrix.  It computed the hamming distance of the input from each column vector prototype of the weight matrix, storing those values in an output vector, equal in width to the weight matrix.  We then constructed the Maxnet which was given the Hammingnet output as a parameter.  It subtracts an epsilon (which we specified as the smallest element in the hamming vector) from each element until a single zero value is found, declaring it the smallest hamming distance.  This index represents the prototype which is most similar to the input, suggesting the input must be of this classification.

\subsection{Image Encoding}
Deciding how to encode our images was a bit tricky.  We played with a few different ways of obtaining image outlines and decided for this network simply finding images already in outline form would be best.  We removed inner detail from these outlines and ran them through a program we wrote.  First, the images are resized so that they are all one standard size,  the images are then grayscaled and run through a threshhold function so that a clear outline of black on white is present.  To establish the prototypes for our weight matrix, we added the values of each representative image matrix to eachother, then averaged the values and processed the result as before.  We adjusted our threshhold function to maintain clarity.  We found that visually, too small a size diminshed image definition, while too large was time and resource intensive and lacked definitive shape for the prototype matrix.

@@

\section{LVQ}
Our LVQ network was created using the Neural Net toolkit for Matlab. We selected a hidden-layer size of [2 * n] to allow the target classes to be created with little room for error in the way of dying centroids based on the order of training. Making use of the built-in training of the toolkit, we simply constructed an input matrix consisting of all of our outlines for each group and made target vectors to use with them. 
\subsection{Image Encoding}
Images were encoded by simply importaing the RGB map, grayscaling, and converting the grayscale 0-255 to -1 and 1 based on a threshold (taken to be 127). These images were also resized to the global size of 64 x 48. The resultant images were those that were thrown into the input matrix and used to train the lvq network.

@@

\subsubsection{Project Report}
Jonathan was tasked with the Hamming/Max section. He also was in charge of reporting on the Overview section.

@@

\subsection{Skyler Manzanares}

\subsubsection{Programming}
Skyler implemented the formatting of centroid images to the weight matrix to be fed into the Hamming/MAX network. He also did extensive work creating the functions that read in and format images. Skyler was also responsible for implementing
the HAM network and the LVQ network.

@@

\subsection{William Fong}
\subsubsection{Programming}
William worked to create the Max layer of the Hamming/Max network and coordinate 
inputs and outputs of the various layers, summing all components together to create a working Hamming/Max network. William was also in charge of implementing the BAM network. He also was in charge of testing his BAM network creation.
\subsubsection{Project Report}
William was tasked to the BAM section and the LVQ analysis section.
